**Title**

### 2018-07-20 manuscript_draft.Rmd
to word

---
title: "**Title**"
author: "$^{1}$Petr Capek*, $^{1}$Katherine Todd-Brown, $^{1}$Natalie Sadler, $^{1}$Nancy Hess, $^{1}$Kirsten Hofmockel"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontfamily: mathpazo
fontsize: 11pt
bibliography: mint.bib
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes:
    - \usepackage{setspace}
    - \doublespacing
    - \usepackage{lineno}
    - \linenumbers
    - \usepackage{titling}
    - \pretitle{\begin{flushleft}}
    - \posttitle{\end{flushleft}}
    - \preauthor{\begin{flushleft}\large}
    - \postauthor{\par\end{flushleft}}
    - \predate{\begin{flushleft}}
    - \postdate{\par\end{flushleft}\vskip 0.5em}
    - \usepackage{float}
    - \floatplacement{figure}{H}

@@

library(knitr)
library(ggplot2)
library(grid)
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)

@@

##Tables
```{r Tab. 1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, results='asis'}
#tab1<-rbind(decay_all_results$likelihood, monod_all_results$ll_r, mem_all_results$ll_r,
            #mend_all_results$ll_r, mmem_all_results$ll_r)
#colnames(tab1)<-c("_Log Likelihood_", "_N_", "_R^{2}_", "_AIC_")
#rownames(tab1)<-c("First order decay", "Monod growth", "MEM", "MEND", "MMEM")
#write.csv(tab1, "./tab1.csv")

tab1<-read.csv("tab1.csv")
colnames(tab1)<-c(" ", "_Log Likelihood_", "_N_", "_R\\textsuperscript{2}_", "_AIC_")

kable(tab1, align='c', digits=c(0, 1, 0, 2, 1), caption = "_Correspondence between measured resiration rate and respiration rate modeled by five different models (First order decay, Monod growth, two different Microbial Enzyme Models (MEM and MEND) and Metabolic Microbial Enzyme Model (MMEM)). Log Likelihood, coefficient of determination ($R^{2}$), Akaike Information Criterion (AIC) and the number of estimated parameters are reported. All models are calibrated against measured respiration rate only._")
```

@@

```{r Scheme 1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

@@

node [shape = circle];
f [label = 'C@_{S}'] ;
g [label = 'C@_{MB}'];
h [label = 'C@_{Enz}'];

@@

grViz(scheme) %>% export_svg() %>% charToRaw %>% rsvg_pdf("scheme.pdf")

include_graphics("scheme.pdf")

>>>>

---
title: "**Title**"
author: "$^{1}$Petr Capek*, $^{1}$Katherine Todd-Brown, $^{1}$Natalie Sadler, $^{1}$Nancy Hess, $^{1}$Kirsten Hofmockel"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontfamily: mathpazo
fontsize: 11pt
bibliography: mint.bib
output: 
  word_document:
    fig_caption: true

@@

library(knitr)
library(ggplot2)
library(grid)
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)
library(kableExtra)
library(magick)

@@

##Tables
```{r Tab. 1, echo=FALSE, fig.width=130, message=FALSE, warning=FALSE, results='asis'}
#tab1<-rbind(decay_all_results$likelihood, monod_all_results$ll_r, mem_all_results$ll_r,
            #mend_all_results$ll_r, mmem_all_results$ll_r)
#colnames(tab1)<-c("_Log Likelihood_", "_N_", "_R^{2}_", "_AIC_")
#rownames(tab1)<-c("First order decay", "Monod growth", "MEM", "MEND", "MMEM")
#write.csv(tab1, "./tab1.csv")

tab1<-read.csv("tab1.csv")

#colnames(tab1)<-c(" ", "Log Likelihood", "N", "$R^{2}$", "AIC")

kable(tab1, align='c', digits=c(0, 1, 0, 2, 1), "latex", booktabs=T, col.names = c(" ", "Log Likelihood", "N", "R^2^", "AIC"), caption = "Correspondence between measured resiration rate and respiration rate modeled by five different models (First order decay, Monod growth, two different Microbial Enzyme Models (MEM and MEND) and Metabolic Microbial Enzyme Model (MMEM)). Log Likelihood, coefficient of determination ($R^{2}$), Akaike Information Criterion (AIC) and the number of estimated parameters are reported. All models are calibrated against measured respiration rate only.") %>%
  kable_as_image()

@@

```{r Scheme 1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width = 20, fig.cap="_Schematic representation of three mathematical models, which are commonly used to predict the respiration rate. $C_{S}$ - carbon substrate, $C_{MB}$ - microbial biomass carbon, $C_{Enz}$ - enzymes carbon._"}

@@

node [shape = circle];
f [label = 'C@_{S}'] ;
h [label = 'C@_{Enz}'];
g [label = 'C@_{MB}'];

@@

grViz(scheme) %>% export_svg() %>% charToRaw %>% rsvg_png("scheme.png")

include_graphics("scheme.png")
